---
title: "R Notebook"
output: 
---

#### Clear Environment
```{r}
rm(list = ls())
```

#### Load Libraries
```{r}
library(tidyverse)
library(dplyr)
library(readxl) 
library(stringr) # string formatting
library(RSQLite) # to connect to SQlite database
library(roxygen2) # For Function Documentation: ctrl + option + shift + r
```

## Load SQLite Database
Create a connection to our new database, CraigslistCars.sqlite3
```{r}
#set path to the database.
db_path <- "/Users/matt/Dev/Projects/MGT6203-grp-project/Database/CraigslistCarsClean.sqlite3"
  
conn <- dbConnect(RSQLite::SQLite(), db_path)
```

#### List of available tables available in the database
```{r}
dbListTables(conn)
```
#### Create DFs called "cars" and "census
```{r}
cars <- dbGetQuery(conn, "SELECT * FROM cars_clean")
census <- dbGetQuery(conn, "SELECT * FROM census_clean")
dbDisconnect(conn)
```

#### View First 6 Rows of 'cars' df
```{r}
head(cars)
```
#Creating New Variable Price/Odometer, we do later, just testing git rn - Shawn
PoverO <- cars %>%
  mutate(pm = cars$price/cars$odometer) 

#Create Linear Regression Model, test
lin <- lm(price ~ year + odometer, data = cars)
summary(lin)

#correlation matrix
correl <- cor(PoverO)
