---
title: "R Notebook"
output: 
---

#### Clear Environment
```{r}
rm(list = ls())
```

#### Load Libraries
```{r}
library(tidyverse)
library(dplyr)
library(readxl) 
library(stringr) # string formatting
library(RSQLite) # to connect to SQlite database
library(roxygen2) # For Function Documentation: ctrl + option + shift + r
library(corrplot)
```

## Load SQLite Database
Create a connection to our new database, CraigslistCars.sqlite3
```{r}
#set path to the database.
db_path <- "CraigslistCarsClean.sqlite3"
  
conn <- dbConnect(RSQLite::SQLite(), db_path)
```

#### List of available tables available in the database
```{r}
dbListTables(conn)
```
#### Create DFs called "cars" and "census"
```{r}
cars <- dbGetQuery(conn, "SELECT * FROM cars_clean")
census <- dbGetQuery(conn, "SELECT * FROM census_clean")
#dbDisconnect(conn)
```

#### View First 6 Rows of 'cars' df
```{r}
head(cars)
```
#Creating New Variable Price/Odometer, we do later, just testing git rn - Shawn
```{r}
#change price type to mutate new column for new variable
cars$price <- as.double(cars$price)
#mutate new variable
PoverO <- cars %>% mutate(pm = cars$price/cars$odometer)
head(PoverO)
```
#Create Linear Regression Model, test
```{r}
lin <- lm(price ~ year + odometer, data = cars)
summary(lin)
```
**Comment** Per result tested on linear regression model above, we can see odometer which has p=0.9 that is greater than typical significant value p=0.05. Thus, it might be not a relevant variable to use. 

#correlation matrix
```{r}
#correl <- cor(PoverO)
#create correlation matrix on cars variables
#corrplot(cars)
```
