---
title: "R Notebook"
output:
  html_document: default
  HTML: default
---

#### Clear Environment

```{r}
rm(list = ls())
```

#### Load Libraries

```{r}
library(tidyverse)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(readxl) 
library(stringr) # string formatting
library(RSQLite) # to connect to SQlite database
library(roxygen2) # For Function Documentation: ctrl + option + shift + r
library(corrplot)
library(ggcorrplot)
library(radiant.data)
library(glue) # to format strings
```

## Load SQLite Database

Create a connection to our new database, CraigslistCars.sqlite3

```{r}
#set path to the database.
db_path <- "Database/CraigslistCarsClean.sqlite3"
  
conn <- dbConnect(RSQLite::SQLite(), db_path)
```

#### List of available tables available in the database

```{r}
dbListTables(conn)
```

Create DFs called "cars" and "census"

```{r}
cars_db <- dbGetQuery(conn, "SELECT * FROM cars_clean")
census_db <- dbGetQuery(conn, "SELECT * FROM census_clean")
dbDisconnect(conn)
```

Create a copy of the Database query so we don't need to re-query each time you want to rerun code.
```{r}
cars <- cars_db
census <- census_db
```

Creating New Variable Price/Odometer, we do later, just testing git rn

```{r}
#Clean cylinder variable
# ifelse(apply(str_contains(cars$cylinders,"cylinders",ignore.case=FALSE)), substring(cars$cylinders,1,1),0)
cars_clean <- cars %>% mutate(cylinders_clean=as.integer(str_extract(cars$cylinders,'[0-9]')))
glimpse(cars_clean)
```

Creating New Variable Price/Odometer

```{r}
#change price type to mutate new column for new variable
cars_clean$price <- as.double(cars_clean$price)
#mutate new variable
cars_clean_pm <- cars_clean %>% mutate(pm = cars$price/cars$odometer)
glimpse(cars_clean_pm)
```

<!-- Select only numeric columns for correlation matrix -->
<!-- ```{r} -->
<!-- car_num <- select_if(cars,is.numeric) -->
<!-- head(car_num) -->
<!-- ``` -->
Correlation matrix for collinearity check

```{r}
cars_clean_pm$fuel <- as.factor(cars_clean_pm$fuel)
cars_clean_pm$title_status <- as.factor(cars_clean_pm$title_status)
cars_clean_pm$transmission <- as.factor(cars_clean_pm$transmission)
cars_sub <- select(cars_clean_pm,year,cylinders_clean,fuel,odometer,title_status,transmission,price)
glimpse(cars_sub)
model.matrix(~0+., data=cars_sub) %>%
  cor(use="pairwise.complete.obs") %>%
  ggcorrplot(show.diag=F,type="full",lab=TRUE, lab_size = 2,ggtheme = ggplot2::theme_gray(),colors = c("#6D9EC1", "white", "#E46726"),tl.srt=90, tl.cex=8, hc.order=TRUE, insig="blank")
# car_num <- select_if(cars,is.numeric)
# head(car_num)
# correl <- cor(car_num[-1])
# corrplot(correl,addCoef.col = 'black')

```

Create Linear Regression Model, test

```{r}
cars$price <- as.double(cars$price)
lin <- lm(price ~ year + odometer, data = cars)
summary(lin)
```

**Comment** Per result tested on linear regression model above, we can see odometer which has p=0.9 that is greater than typical significant value p=0.05. Thus, it might be not a relevant variable to use.

Plot scatter/residual plots to spot non-linearity and outliers/high-leverage points

```{r}
plot(lin,which=1:5)
```

Plot price trends in different states of USA

```{r}
price_trend <- cars_clean_pm %>% group_by(state) %>%summarize(average_price=mean(price))
ggplot(price_trend, aes(x=reorder(state,-log(average_price)),y=log(average_price))) + geom_bar(stat="identity",fill="steelblue") + labs(x="state") 
```

Plot box-plot to detect outliers/influential points across US states

```{r}
ggplot(cars_clean_pm,aes(x=state,y=log(price))) + geom_boxplot(fill="steelblue")
```

Market share of TOP 10 manufacturers

```{r}
top_10 <- cars %>% group_by(manufacturer) %>% summarize(count=n()) %>% arrange(desc(count)) %>% top_n(10)
top_10
ggplot(top_10,aes(x=reorder(manufacturer,-count),y=count)) + geom_bar(stat='identity',fill='steelblue') + labs(x="Manufacturer")
```

Type of car and fuel

```{r}
car_type <- cars %>% group_by(fuel,type) %>% summarize(count=n()) %>% arrange(desc(count)) %>% top_n(10)
car_type
ggplot(car_type,aes(fill=fuel,x=reorder(type,-count),y=count)) + geom_bar(stat="identity",position="stack") + labs(x="Type")
```

Condition vs Year relationship

```{r}
ggplot(cars,aes(x=year,y=condition)) + geom_violin(scale='area',fill='steelblue') + geom_boxplot(width=0.1,colors='grey',alpha=0.2)
```

Odometer vs Price relationship

```{r}
ggplot(cars, aes(x=log(odometer),y=log(price)*1000,color=year))+geom_point() + labs(x='odometer',y='price') 
```


Convert 'state' column to upper case and convert 'posting_date' to DT
```{r}
cars$state <- str_to_upper(cars$state)
cars$posting_date <- as.POSIXct(cars$posting_date)
```

Create single city average from Census data to so we can join to cars
```{r}
census_grouped <- census %>% 
  group_by(city, state) %>% 
  summarise(med_family_income = median(median_income_family),
            med_non_family_income = median(median_income_non_family))
```


Merge 'cars' and 'census'
```{r}
cars <- left_join(cars, census_grouped, by = c("state", "city"))
```

```{r}
Odometer_Filter <- function (df, start_year, mileage, remove_na = TRUE) {

  df <- df %>% filter(!is.na(odometer))
  
  mileage_filter <- (df$year <= start_year & df$odometer < mileage)
  df <- df %>% filter(!mileage_filter)
          
  return(df)
  
#' Title: odometer_filter 
#'
#' @param df - dataframe
#' @param start_year - ex: 2018 -> filter out all cars before 2018
#' @param mileage - ex: 500 -> filter out cars with odometer values < 500
#' @param remove_na = TRUE {default}. This removes all NA values from the df
#'
#' @return a dataframe with applied filters
#'
#' @examples odometer_test <- odometer_filter(cars_test, 2018, 500)
  
}
```

```{r}
odometer_test <- Odometer_Filter(cars, 2018, 50)
```

View First 6 Rows of 'cars' df

```{r}
head(cars)
```

<<<<<<< HEAD
#### Create 'age' column
=======
Create 'age' column
>>>>>>> bcad500565768088f9bb22bbfaa0291a0d9a8f30
```{r}
cars$age <- 2021 - cars$year
```

Convert 'state', 'manufacturer', 'model' to factor datastructure
```{r}
cars$state.x <- cars$state %>% factor()
cars$manufacturer <- cars$manufacturer %>% factor()
cars$fuel <- cars$fuel %>% factor()
cars$transmission <- cars$transmission %>% factor()
cars$type <- cars$type %>% factor()
cars$paint_color <- cars$paint_color %>% factor()
cars$drive <- cars$drive %>% factor()
cars$title_status <- cars$title_status %>% factor()
```

Convert 'condition' to ordered factor
```{r}
cars %>% count(condition)
```

```{r}
condition_order <- c('unknown', 'salvage', 'fair', 'good', 'excellent', 'like new', 'new')
cars$condition <- cars$condition %>% factor(levels = condition_order)
```

Clean "cylinder" Variable

```{r}
#- convert to ordered factor data structure
cars %>% count(cylinders)
```

```{r}
cylinder_levels <- c("un", "3", "4", "5", "6", "8", "10", "12")

cars$cylinders <- factor(str_trim(substr(cars$cylinders, start = 1, stop = 2)), levels = cylinder_levels)
cars %>% count(cylinders)
```
Convert Price to Numeric
```{r}
cars$price <- cars$price %>% as.double()
```

Open DF in Radiant for Exploratory Analysis and Modeling
```{r}
#radiant::radiant()
```

```{r}
manuf_bar_plot <- cars %>% 
  group_by(manufacturer) %>% 
  summarise(count = n()) %>% 
  filter(count > 1000) %>% 
  ggplot(aes(x = reorder(manufacturer, (count)), y = count)) + 
    #theme(aspect.ratio = .6) +
    theme(plot.margin = unit(c(.5,.5,.5,.5), "cm")) +
    geom_bar(stat = "identity", width = .5, fill = "cadetblue3") + 
    labs(x = "Manufacturer", y = "Count", title = "Count of Manufacturers") +
    ylim(c(0,80000)) + 
    coord_flip()

# aspect_ratio <- 2.5
# height <- 9
# ggsave("manuf_bar_plot.png", plot = manuf_bar_plot, width = 7 * aspect_ratio, height = 7, units = "in", dpi = 300)

plot(manuf_bar_plot)
```
```{r}
cars %>% filter(manufacturer == "Ford") %>% 
  count(model)
```


```{r}
ford_models_pattern <- paste(c("Figo", "Fusion Energi", "Focus Electric", "Fiesta", "Endura",
                               "C-Max Hybrid", "B-Max", "Flex", "i-Max", "Fusion", "LCF",
                               "Excursion", "Ikon", "Focus", "Maverick", "Explorer Sport Trac",
                               "Activa", "SportKa", "Freestar", "Territory", "Five Hundred", 
                               "Aspire", "Contour", "Cougar", "Crown Victoria", "Freda", 
                               "Galaxy", "Ka", "Tourneo", "Puma", "Windstar", "ZX2", "F150", 
                               "F-150", "F250", "F-250", "F350", "F-350", "Ranger", "Aerostar",
                               "Bronco", "Bronco II", "Escort", "Probe", "Sierra", "Telstar",
                               "Taurus", "Tempo", "Verona", "Falcon", "F 150", "F 250", "F 350",
                               "F450", "F 450", "F-450", "F750", "F 750", "F-750", "F100", 
                               "F 100", "F-100", "Escape", "Sport Trac", "C Max", 
                               "Thunderbird", "Expedition", "Model B","Model T", "Model Y", 
                               "Model C", "Model A", "Mustang", "Explorer", "Econoline",
                               "Crown Vic", "Transit", "Freestyle", "E350", "E 350", "E-350",
                               "Edge", "F 550", "F-550", "F550", "E150", "E 150", "E-150",
                               "E250", "E 250", "E-250", "E450", "E 450", "E-450",
                               "Ecosport", "F650", "F-650", "F 650", "Raptor", "150", "250",
                               "350", "450"), collapse = "|")

                             
ford <- cars %>%
  filter(manufacturer == "Ford") %>% 
  mutate(model_clean = str_extract(model, regex(pattern = ford_models_pattern, ignore_case = TRUE)))    
```

```{r}
f_150 <- paste(c("F150", "F-150", "F 150", "F-150"), collapse = "|")
f_250 <- paste(c("F250", "F-250", "F 250", "F-250"), collapse = "|")
f_350 <- paste(c("F350", "F-350", "F 350", "F-350"), collapse = "|")
f_450 <- paste(c("F450", "F-450", "F 450", "F-450"), collapse = "|")
f_550 <- paste(c("F550", "F-550", "F 550", "F-550"), collapse = "|")

ford$model_clean <- str_replace_all(ford$model_clean, regex(pattern = f_150), "F-150")
ford$model_clean <- str_replace_all(ford$model_clean, regex(pattern = f_250), "F-250")
ford$model_clean <- str_replace_all(ford$model_clean, regex(pattern = f_350), "F-350")
ford$model_clean <- str_replace_all(ford$model_clean, regex(pattern = f_450), "F-450")
ford$model_clean <- str_replace_all(ford$model_clean, regex(pattern = f_550), "F-550")
```


```{r}
ford_clean <- ford %>% 
<<<<<<< HEAD
  filter(!is.na(model_clean) & price < 100000) %>% 
=======
  filter(!is.na(model_clean) & price < 100000)

ford_model_hist <- ford_clean %>% 
  group_by(model_clean) %>% 
  summarise(count = n(), price = price) %>% 
  filter(count > 500) %>% 
  ggplot(aes(x = price, y = model_clean, color = model_clean)) +
  geom_boxplot() +
  labs(title = "Ford Models - Boxplot", y = "Model", x = "Price", color = "Model")
    
  
plot(ford_model_hist)
```

Study cars statistics
>>>>>>> c2a12af87de95e4c01bb776f51ed11a7970a419c

```{r}
ford_df <- ford_clean %>%
>>>>>>> bcad500565768088f9bb22bbfaa0291a0d9a8f30
  mutate(model_clean = as.factor(model_clean)) %>% 
  select(city, state, manufacturer, model_clean, age, condition, cylinders, fuel, odometer,
         title_status, transmission, drive, type, paint_color, price, 
         med_family_income, med_non_family_income)

```
<<<<<<< HEAD


```{r}
#' Title: Model_Box
#'
#' @param input_manufacturer {string}
#'
#' @return: box plot
#' @export: box plot
#'
#' @examples: Model_Box("Ford")
#' 
#' 
Model_Box <- function(input_manufacturer){
  
  # Connect to the database
  conn <- dbConnect(RSQLite::SQLite(), db_path)
  df <- dbGetQuery(conn, glue("SELECT model_clean, price
                               FROM {input_manufacturer}"))
  # Close db connection
  dbDisconnect(conn)
  
  # Build box plots
  model_box <- df %>% 
    group_by(model_clean) %>% 
    summarise(count = n(), price = price) %>%
    # Filter out vehicles that have limited number of observations
    filter(count > 500) %>% 
    ggplot(aes(x = price, y = model_clean, color = model_clean)) +
    geom_boxplot() +
    labs(title = glue("{input_manufacturer} Models - Boxplot"), 
         y = "Model", 
         x = "Price", 
         color = "Model")
  
  # Return Plot
  plot(model_box)
  
}
```

```{r}
Model_Box("Ford")
```

#### Create a function to predict prices for Ford models based on a series of inputs:
=======
Create a function to predict prices for Ford models based on a series of inputs:
>>>>>>> bcad500565768088f9bb22bbfaa0291a0d9a8f30
- state
- manufacturer
- model
- year
- odometer
- condition

```{r}
#' Title: Model_Prediction
#'
#' @param input_state {string}
#' @param input_city {string}
#' @param input_manufacturer {string} 
#' @param model {string}
#' @param year {int}
#' @param odometer {int}
#' @param input_condition {string} 
#' @param drive {string}
#' @param cylinders {string}
#'
#' @return
#' @export
#'
#' @examples
#' 
Model_Prediction <- function(input_state, input_city, input_manufacturer, model, 
                             year, odometer, input_condition, drive, cylinders) {
  
  # Connect to db and create df based on input_manufacturer
  conn <- dbConnect(RSQLite::SQLite(), db_path)
  df <- dbGetQuery(conn, glue("SELECT state, city, manufacturer, model_clean, age, condition, 
                                      odometer, drive, cylinders, price, med_family_income, med_non_family_income
                               FROM {input_manufacturer}"))
  # Close db connection
  dbDisconnect(conn)
  
  # Create a df filtered by input state, manufacturer, and model
  df <- df %>%
    filter(state == input_state, 
           manufacturer == input_manufacturer, 
           model_clean == model,
           condition == input_condition
    )
  
  # Extract income values for model 
  med_inc <- df %>% filter(state == input_state, city == input_city)
  med_inc_fam <- med_inc$med_family_income[1]
  med_inc_non_fam <- med_inc$med_non_family_income[1]
  
  # Create linear model
  lm_model <- lm(price ~ age + odometer + drive + cylinders + med_family_income + med_non_family_income, data = df)
  
  # Create new data point from user inputs
  newData <- data.frame(model_clean = model,
                        age = 2021 - year,
                        odometer = odometer,
                        drive = drive,
                        cylinders = cylinders,
                        med_family_income = med_inc_fam,
                        med_non_family_income = med_inc_non_fam)
  
  # Create list of objects to return as list
  number_of_observations <- paste("Number of Training Observations = ", nrow(df))
  model_summary <- summary(lm_model)
  predictions <- predict(lm_model, newdata = newData, interval = "confidence", level = .95)
  
  
  return(list(number_of_observations, model_summary, predictions))
  
}

```

<<<<<<< HEAD
#### Test 'ford_prediction' Function
=======
Test 'ford_prediction' Function
>>>>>>> bcad500565768088f9bb22bbfaa0291a0d9a8f30
```{r}
Model_Prediction("CA", "Sacramento", "Ford", "F-250", 2015, 100000, "good", "4wd", "8")
```


<<<<<<< HEAD
#Creating New Variable Price/Odometer, we do later, just testing git rn - Shawn

#Clean cylinder variable

```{r}
#ifelse(apply(str_contains(cars$cylinders,"cylinders",ignore.case=FALSE)), substring(cars$cylinders,1,1),0)
cars_clean <- cars %>% mutate(cylinders_clean=as.integer(str_extract(cars$cylinders,'[0-9]')))
glimpse(cars_clean)
```

#Creating New Variable Price/Odometer

```{r}
#change price type to mutate new column for new variable
cars_clean$price <- as.double(cars_clean$price)
#mutate new variable
cars_clean_pm <- cars_clean %>% mutate(pm = cars$price/cars$odometer)
glimpse(cars_clean_pm)
```

#select only numeric columns for correlation matrix
```{r}
car_num <- select_if(cars,is.numeric)
head(car_num)
```

#correlation matrix for collinearity check

```{r}
cars_clean_pm$fuel <- as.factor(cars_clean_pm$fuel)
cars_clean_pm$title_status <- as.factor(cars_clean_pm$title_status)
cars_clean_pm$transmission <- as.factor(cars_clean_pm$transmission)
cars_sub <- select(cars_clean_pm,year,cylinders_clean,fuel,odometer,title_status,transmission,price)
glimpse(cars_sub)
model.matrix(~0+., data=cars_sub) %>%
  cor(use="pairwise.complete.obs") %>%
  ggcorrplot(show.diag=F,type="full",lab=TRUE, lab_size = 2,ggtheme = ggplot2::theme_gray(),colors = c("#6D9EC1", "white", "#E46726"),tl.srt=90, tl.cex=8, hc.order=TRUE, insig="blank")
# car_num <- select_if(cars,is.numeric)
# head(car_num)
# correl <- cor(car_num[-1])
# corrplot(correl,addCoef.col = 'black')

```

#Create Linear Regression Model, test

```{r}
cars$price <- as.double(cars$price)
lin <- lm(price ~ year + odometer, data = cars)
summary(lin)
```

**Comment** Per result tested on linear regression model above, we can see odometer which has p=0.9 that is greater than typical significant value p=0.05. Thus, it might be not a relevant variable to use.

#plot scatter/residual plots to spot non-linearity and outliers/high-leverage points

```{r}
plot(lin,which=1:5)
```

#plot price trends in different states of USA

```{r}
price_trend <- cars_clean_pm %>% group_by(state) %>%summarize(average_price=mean(price))
ggplot(price_trend, aes(x=reorder(state,-log(average_price)),y=log(average_price))) + geom_bar(stat="identity",fill="steelblue") + labs(x="state") 
```

#Plot box-plot to detect outliers/influential points across US states

```{r}
ggplot(cars_clean_pm,aes(x=state,y=log(price))) + geom_boxplot(fill="steelblue")
```

#Market share of TOP 10 manufacturers

```{r}
top_10 <- cars %>% group_by(manufacturer) %>% summarize(count=n()) %>% arrange(desc(count)) %>% top_n(10)
top_10
ggplot(top_10,aes(x=reorder(manufacturer,-count),y=count)) + geom_bar(stat='identity',fill='steelblue') + labs(x="Manufacturer")
```

#Type of car and fuel

```{r}
car_type <- cars %>% group_by(fuel,type) %>% summarize(count=n()) %>% arrange(desc(count)) %>% top_n(10)
car_type
ggplot(car_type,aes(fill=fuel,x=reorder(type,-count),y=count)) + geom_bar(stat="identity",position="stack")
```

#Condition vs Year relationship

```{r}
ggplot(cars,aes(x=year,y=condition)) + geom_violin(scale='area',fill='steelblue') + geom_boxplot(width=0.1,colors='grey',alpha=0.2)
```

#Odometer vs Price relationship

```{r}
ggplot(cars, aes(x=log(odometer),y=log(price)*1000,color=year))+geom_point() + labs(x='odometer',y='price') 
```
=======




>>>>>>> bcad500565768088f9bb22bbfaa0291a0d9a8f30
