---
title: "Model Comparison"
author: "Jason Young"
date: "4/23/2022"
output: html_document
---

### Contents of this Workbook
1. Setup

2. Define the the Model_Comparision() Function

3. Apply to Various Regression Models


#### 1. Setup
Clear Enviromnet & Load Libraries 

```{r}
rm(list = ls()) # Clear Enviromnemt
library(tidyverse)
library(dplyr)
library(readxl) 
library(stringr) # string formatting
library(RSQLite) # to connect to SQlite database
library(glmnet)
```

### 2. Define the Model_Comparison() Function
Takes 1 dataframe and any number of models to compare
Splits the datframe into train, validation, and test sets
Trains each model on the training data
Compares each model using the validation data and selects the best one
Evaluates the best model with the test set
Prints a dataframe comparing accuracy metrics

    the funtion takes 2 arguments
      1st arg is the data frame to be used for train/test/validate
      
      2nd arg is a list of lists where:
        the first entry is a string "model_name"
        the second entry is a function to build the model from the data frame
      
      For Example:
        
        Model_Comparison( cars_df,
                          [ ("LM #1", model_creation_function() ),  
                            ("LM #2", model_creation_function() ), 
                            ("KNN #1", model_creation_function() 
                          ]
                        )  
    


```{r}
Model_Comparison <- function(df, list_of_tuples)
{  
  # split dataframe into training, validation, and test sets (60-20-20% rule)         
  train_size = round(0.6 * nrow(df), 0)
  valid_size = round(0.2 * nrow(df), 0)
  test_size = round(0.2 * nrow(df), 0)
  shuffled_rows <- sample(nrow(df)) 
  df = df[shuffled_rows, ]
  train_data = df[1:train_size, ]
  valid_data = df[(train_size + 1):(train_size + valid_size), ] 
  test_data = df[(train_size + valid_size + 1):nrow(df), ]
  
  # Create the empty output dataframe for comparison
  output_df <- data.frame(matrix(ncol = 4, nrow = 0))
  colnames(output_df) <- c("Model", "R^2 on Validation Data", "Best Model?", "R^2 on Test Data")
  
  # Create empty lists to collect R^2 values
  R_2_list = c()
  best_R_2_list = c()
  
  # For each model provided:
  for (i in 1:length(list_of_tuples))
  {
    # Use training set to create the model
    mod = tuple_list[[i]][[2]](train_data)
  
    # Use the model to predict values on the validation set and collect the SSE in a list
    predictions = predict(mod, valid_data)
    SSR = sum((predictions - valid_data$price)^2)
    SST = sum((valid_data$price - mean(valid_data$price))^2)
    R_2 = round(1 - SSR/SST, 3)
    R_2_list = c(R_2_list, R_2)
    
    # Use model to predict values on the test set (used for the final selected model)
    predictions = predict(mod, test_data)
    SSR = sum((predictions - test_data$price)^2)
    SST = sum((test_data$price - mean(test_data$price))^2)
    R_2 = round(1 - SSR/SST, 3)
    best_R_2_list = c(best_R_2_list, R_2)
    
  }
  
  # Determine the best model, based on smallest SSE on the validation set
  best = which(R_2_list == max(R_2_list))
  best_R_2 = rep(0, length(list_of_tuples))
  best_R_2[[best]] = 1
  
  
  # Report Test Accuracy for best model
  test_acc = c()
  for (i in 1:length(list_of_tuples))
  {
    if (best_R_2[[i]] == 0){
      test_acc = c(test_acc, NA)}
    else{
      test_acc = c(test_acc, best_R_2_list[[i]])
    }
  }
  
  # Populate the final output dataframe, using values collected above
  #   and print it
  for (i in 1:length(list_of_tuples))
  {
  output_df[nrow(output_df) + 1,] = c(tuple_list[[i]][[1]], #Name Column
                                      R_2_list[[i]],  #SSE on Validation
                                      best_R_2[[i]],  #1=best model, 0=all others
                                      test_acc[[i]])
  }
  print("Trained on:")
  print(train_size)
  print(output_df)
  
}  



```



### 3. Apply Model_Comparison to Various Regression Models


### First, prepare the dataset and perform some basic cleaning

```{r}
# Create Path to SQLite db

db_path <- "CraigslistCarsClean.sqlite3"

# Establish connection
conn <- dbConnect(RSQLite::SQLite(), db_path)
cars <- dbGetQuery(conn, "SELECT * FROM Ford A LEFT JOIN outdoor_rec_by_state B on (A.state = upper(B.state))")

names(cars)[names(cars) == 'Percent of total wage and salary employment1'] <- 'perc_outdoor_employment'
names(cars)[names(cars) == 'Percent of total compensation1'] <- 'perc_total_comp'

# Close db connection
dbDisconnect(conn)

Add_Regions <- function (df) {
  
  # Create 9 different regions of the country
  southwest <- c("CA", "AZ", "NM", "HI","NV")
  west <- c("UT", "CO", "WY", "MT", "ND", "SD")
  pnw <- c("AK", "OR", "ID", "WA")
  n_east <- c("CT", "ME", "MA", "NH", "RI", "VT")
  east <- c("NJ", "NY", "DE", "MD", "PA", "VA", "DC", "WV")
  s_east <- c("AL", "FL", "GA", "KY", "MS", "NC", "SC", "TN")
  midwest <- c("IL", "IN", "MI", "MN", "OH", "WI")
  south <- c("TX", "AR", "LA", "OK")
  central <- c("IA", "KS", "MO", "NE")
  
  # Add Regions to cars DF
  df <- df %>%
    mutate(region = case_when(state %in% southwest ~ "Southwest", 
                              state %in% west ~ "West",
                              state %in% pnw ~ "Pacific Northwest",
                              state %in% n_east ~ "Northeast",
                              state %in% east ~ "East",
                              state %in% s_east ~ "Southeast",
                              state %in% midwest ~ "Midwest",
                              state %in% south ~ "South",
                              state %in% central ~ "Central"
                              )
           )
  
 return(df) 
  
}

# Add regions to 'cars' df
cars <- Add_Regions(cars)


Clean_Drive <- function(df){
  awd <- paste(c("awd", "awD", "Awd", "AwD", "AWD"), collapse = "|")
  rwd <- paste(c("rwd", "RwD", "Rwd", "rwD", "RWD"), collapse = "|")
  fwd <- paste(c("fwd", "FwD", "fWD", "fwD", "FWD", "Fwd"), collapse = "|")
  fourwheeldrive <- paste(c("4wd", "4wD", "4WD", "4wD", "4Wd"), collapse = "|")
  
  df$drive <- str_replace_all(df$drive, regex(pattern = awd), "AWD")
  df$drive <- str_replace_all(df$drive, regex(pattern = rwd), "RWD")
  df$drive <- str_replace_all(df$drive, regex(pattern = fwd), "FWD")
  df$drive <- str_replace_all(df$drive, regex(pattern = fourwheeldrive), "4WD")
  
  return(df)
}

##------------------------------------
##  Test Clean_Drive() Function  --
##------------------------------------
cars <- Clean_Drive(cars)


### filter out a few models in bad format
cars = cars[!(cars$model %in% c("Aspire", "fusion", "Ka", "f 150", "Tempo", "f150", "taurus", "f 550", "f350", "450", "e 550", "Probe", "e 250", "Model B", "thunderbird", "Maverick")), ]

### filter a few cities in bad format and too many cylnders
cars = cars[!(cars$city %in% c("Meridian", "Oneonta")), ]
cars = cars[!(cars$cylinders %in% c(12)), ]

head(cars)


```


### Next, Create models's and run Model_Comparison() to select the best model and get test its accuracy


```{r}

standard_lm_function_car_only = function(df)
{
  lm_model <- lm(price ~ model + fuel + type + condition + age + odometer + drive + cylinders + paint_color
, data = df)
  return (lm_model)
}

standard_lm_function = function(df)
{
  lm_model <- lm(price ~   city + state + model + fuel + type + condition + age + odometer + drive + cylinders + paint_color + region + med_family_income + med_non_family_income + perc_outdoor_employment + perc_total_comp
, data = df)
  return (lm_model)
}

standard_lm_log_age = function(df)
{
  lm_model <- lm(price ~ city + state + model + fuel + type + condition + log(age+2) + odometer + drive + cylinders + paint_color + region + med_family_income + med_non_family_income + perc_outdoor_employment + perc_total_comp, data = df)
  return (lm_model)
}

log_age_log_odometer = function(df)
{
  lm_model <- lm(price ~ city + state + model + fuel + type + condition + log(age+2) + log(odometer+1) + drive + cylinders + paint_color + region + med_family_income + med_non_family_income + perc_outdoor_employment + perc_total_comp, data = df)
  return (lm_model)
}


tuple_list =
  list(
    list("Standard LM (car info only)", standard_lm_function_car_only),
    list("Standard LM plus local economic data", standard_lm_function),
    list("Log Age (All Columns)", standard_lm_log_age),
    list("Log Age Log Odometer (All Columns)", log_age_log_odometer)
  )


Model_Comparison(cars, tuple_list)

```

```{r}

model_for_interpretation = function(df)
{
  lm_model <- lm(price ~ fuel + type + condition + log(age+2) + log(odometer+1) + drive + cylinders + paint_color + region + med_family_income + med_non_family_income + perc_outdoor_employment + perc_total_comp, data = df)
  return (lm_model)
}

best_model = model_for_interpretation(cars)

summary(best_model)

```
